Finding Subgraphs With Side Constraints\thanks{This research was supported by the Engineering and Physical Sciences Research Council [grant number EP/P026842/1]}

### 2021-04-20 paper/paper.tex
Better line breaks, and code

@@

Unfortunately, whilst elegant and flexible, the performance of this approach leaves a lot to be
desired on basic subgraph isomorphism instances.  The computational experiments in this paper are
performed on a cluster of machines with dual Intel Xeon E5-2697A v4 processors and 512GBytes RAM
running Ubuntu 18.04. The source code used for these experiments is released as part of the Glasgow
Subgraph
Solver\footnote{\url{https://github.com/ciaranm/glasgow-subgraph-solver/releases/tag/cpaior2021-finding-subgraphs-with-side-constraints}},
Minion\footnote{\url{https://github.com/minion/minion/releases/tag/1.9}}, and
Conjure\footnote{\url{https://github.com/conjure-cp/conjure}} distributions.

>>>>

% url by default does horrible things with line breaks, this makes it behave better
\usepackage{xurl}

@@

Unfortunately, whilst elegant and flexible, the performance of this approach leaves a lot to be
desired on basic subgraph isomorphism instances.  The computational experiments in this paper are
performed on a cluster of machines with dual Intel Xeon E5-2697A v4 processors and 512GBytes RAM
running Ubuntu 18.04. The source code used for these experiments is released as part of the Glasgow
Subgraph
Solver\footnote{\url{https://github.com/ciaranm/glasgow-subgraph-solver/releases/tag/cpaior2021-finding-subgraphs-with-side-constraints}},
Minion\footnote{\url{https://github.com/minion/minion/releases/tag/1.9}}, and
Conjure\footnote{\url{https://github.com/conjure-cp/conjure}} distributions, and we provide a
separate archive for experimental
scripts\footnote{\url{https://github.com/ciaranm/cpaior2021-finding-subgraphs-with-side-constraints}}.
